DRAFT: Harmonized and trait aggregation paper

### 2020-10-25 Paper/Results/Results_trait_harmonization.tex
Removed comments and moved to overleaf review section
25.10: Minor updates

For every aggregation method compared, using at family-level aggregated traits did only slightly change the species scores compared to not aggregated traits (Figure \ref{fig:rda_species_scores}). 
% Hence, the interpretation of the trait composition is the same as when only using harmonized grouping features. 
%? Mention that threshold according to mahalanobis distance is almost reached for life cycle duration

% Species scores
\begin{figure}[H]
    \label{fig:rda_species_scores}
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
    \caption{Species scores obtained by RDA from the original analysis \cite{szocs_effects_2014}, using harmonized grouping features, and using harmonized grouping features with assigned trait affinities aggregated to family-level.}
    \label{fig:rda_species_scores}
\end{figure}

% PUP comment: 
% What are exactly „RDA species scores“? The coordinates of species along the first factorial axis in RDA?
% If „yes“, I’m not sure this result presentation is suitable. In fact the box-plots summarizing the distributions of the set of species in the RDA analysis, after applying different strategies of trait description, can be very similar (it’s not surprising, because in each case the mean coordinate of species is 0), but the individual locations of species along each axis can be very different from an RDA to another axis (i.e. from a grouping feature definition strategy to another). It would be probably far more interesting to represent the distribution of deviations between the RDA scores provided by each strategy and the original RDA scores (from Szöcs et al., 2018)..

>>>>

For every aggregation method compared, using at family-level aggregated traits did only slightly change the species scores compared to not aggregated traits (Figure \ref{fig:rda_species_scores}).

\begin{figure}[H]
    \label{fig:rda_species_scores}
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
    \caption{Species scores obtained by RDA from the original analysis \cite{szocs_effects_2014}, using harmonized grouping features, and using harmonized grouping features with trait affinities aggregated to family-level.}
    \label{fig:rda_species_scores}
\end{figure}
